The problem and promise of scale in multilayer animal social networks

### 2020-06-15 paper/manuscript.Rmd
Revert "minor change - practice push on q branch"
This reverts commit cb306a2d1f8a5d3f27f02bc6f1e73a63b70031b5.

Multilayer networks provide unique opportunities and challenges, linking
various scales, for understanding the social phenotypes and environments of
individuals and their fitness outcomes. The multilayer network framework enables
researchers to examine these different social scales simultaneously rather than
individually, which is what has been done under most circumstances, but is not
very realistic. Metrics from multilayer networks provide an opportunity to
simplify statistical models. Interactions that happen side-by-side, proximity
associations, and long-distance interactions can be encapsulated in a single
multilayer network, and a single metric can be used to describe the various
social scales of an individual’s network position. This multilevel network
metric could be used to assess the relationship between an individual’s social
phenotype and fitness. It would also be a meaningful reduction of many
network metrics that could help simplify statistical analyses and deal with the
frequent correlations between social network metrics in different types of
networks [@Castles_2014]. Furthermore, multilayer networks provide a framework
to test hypotheses linking social phenotypes and fitness across temporal scales.
Because of the non-independent nature of social interactions and associations,
especially over time, it is hard to test hypotheses about social dynamics with a
suitable null control [@Farine_2017; @Proskurnikov_2017]. Using the framework of
multilayer networks, making layers of different temporal periods provides a way
to make appropriate null models to test questions about the dynamics of an
individual’s social network position over multiple aggregated time periods.

>>>>

Multilayer networks provide unique opportunities and challenges, linking these
various scales, for understanding the social phenotypes and environments of
individuals and their fitness outcomes. The multilayer network framework enables
researchers to examine these different social scales simultaneously rather than
individually, which is what has been done under most circumstances, but is not
very realistic. Metrics from multilayer networks provide an opportunity to
simplify statistical models. Interactions that happen side-by-side, proximity
associations, and long-distance interactions can be encapsulated in a single
multilayer network, and a single metric can be used to describe the various
social scales of an individual’s network position. This multilevel network
metric could be used to assess the relationship between an individual’s social
phenotype and fitness. It would also be a meaningful reduction of many
network metrics that could help simplify statistical analyses and deal with the
frequent correlations between social network metrics in different types of
networks [@Castles_2014]. Furthermore, multilayer networks provide a framework
to test hypotheses linking social phenotypes and fitness across temporal scales.
Because of the non-independent nature of social interactions and associations,
especially over time, it is hard to test hypotheses about social dynamics with a
suitable null control [@Farine_2017; @Proskurnikov_2017]. Using the framework of
multilayer networks, making layers of different temporal periods provides a way
to make appropriate null models to test questions about the dynamics of an
individual’s social network position over multiple aggregated time periods.
